\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{listings}
\usepackage[T1]{fontenc}
\usepackage{geometry}

\geometry{
 a4paper,
 left=20mm,
 right=20mm,
 top=20mm,
 bottom=20mm
 }

\lstset{
    language=C,
    showstringspaces=false,
    breaklines=true
}


\title{ME 333 Quiz 4: Chapter 4}
\author{Marshall Johnson}
\date{February 3, 2022}

\begin{document}

\maketitle

\section*{Quiz 4}

\begin{enumerate}[label=\textbf{\arabic*})]
    \item \textbf{What is the purpose of the NU32\_Startup() function?} \\
    
    The NU32\_Startup() function configures the PIC32 and NU32 library. The process includes
    the following tasks: \\
    \begin{enumerate}
        \item configures prefetch cache module and flash wait cycles for maximum performance
        \item configures PIC32 for multi-vector interrupt mode
        \item disables JTAG debugging 
        \item configures RF0 and RF1 as digital outputs
        \item configures UART3
        \item enables interrupts
    \end{enumerate}

    \item \textbf{Why doesn’t the following command work as intended?  \\
    LCD\_WriteString(“Hello world 12345678”)} \\

    The LCD only takes 16 characters per line. Since the string input here is more than 16 characters,
    some will not be displayed.

    \item \textbf{What does the command line instruction make clean do?} \\
    
    This command removes the files that were created when the project was initially built. This
    allows \textit{make} to be run again from scratch.



\end{enumerate}



\end{document}
