\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{listings}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amsmath}

\geometry{
 a4paper,
 left=20mm,
 right=20mm,
 top=20mm,
 bottom=20mm
 }

\lstset{
    language=C,
    showstringspaces=false,
    breaklines=true
}


\title{ME 333 Quiz 7 \\ [1ex] \large PID Control}
\author{Marshall Johnson}
\date{February 24, 2022}

\begin{document}

\maketitle

\section*{Quiz 7}

\begin{enumerate}[label=\textbf{\arabic*})]
    \item \textbf{Give pseudocode for a basic PID controller (without integrator anti-windup). 
    There are functions get\_ref() and get\_sensor() to call, and you can make others if you want. 
    There are already global variables, and you can add more: \\
    static volatile float eint = 0; \\ 
    static volatile float eprevious = 0; \\  
    The ISR is already setup to run at 1kHz:} \\

     \begin{lstlisting}

        static volatile float err = 0;
        static volatile float edot = 0;
        static volatile float u = 0;
        static volatile float s = 0;
        static volatile float r = 0;
        __ISR(timer at 1kHz) {
            s = get_sensor();               // read sensor value
            r = get_ref();                  // get reference signal
            err = r - s;                    // calculate error
            edot = err - errprevious;       // error difference
            eint = eint + err;              // error sum
            u = Kp*err + Ki*eint + Kd*edot; // calculate control signal
            send_control(u);                // send control signal
            eprevious = err;                // update error
            interrupt_flag = 0;             // clear interrupt flag
        }
     \end{lstlisting}

     \item \textbf{Explain what integrator anti-windup is: } \\
     
     When integrator error is allowed to build up to large values, a large control signal
     of opposite sign is created to dissipate the error. To reduce oscillation associated
     with this behavior, \textbf{integrator anti-windup} can be implemented by placing 
     bounds on the integrator error (\textit{eint}).

     \item \textbf{You have picked Kp, Ki, and Kd gains. } \\
     
     \begin{enumerate}[label=\textbf{\alph*}.]
        \item \textbf{The response has too much overshoot. Which gain could you increase to reduce the 
        overshoot?} \\

        $K_{d}$

        \item \textbf{The response has too much overshoot. Which gain could you decrease to reduce the 
        overshoot?} \\

        $K_{p}$

        \item \textbf{The response has the right overshoot and settling time characteristics, but too much 
        steady-state error. Which gain could you increase to reduce the steady-state error?} \\

        $K_{p}$
     \end{enumerate}

    
    
\end{enumerate}



\end{document}
